Estimating Comparative Advantage in Improved Seed Adoption: Hybrid Maize in Ethiopia

### 2021-11-24 paper.tex
Updates from Overleaf

\usepackage{natbib}
\bibliographystyle{rusnat}

@@

\begin{figure}
    \centering
    \includegraphics{results/figures/map_hhids.pdf}
    \caption{Spatial Distribution of Households Surveyed}
    \label{map:regions}
\end{figure}

Table \ref{tbl:summary} shows a set of summary statistics for our sample.

>>>>

\usepackage{natbib}
\bibliographystyle{rusnat}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{caption}

@@

\begin{figure}
    \centering
    \includegraphics{results/figures/map_hhids.pdf}
    \caption{Spatial Distribution of Households Surveyed}
    \figcaption{Note: Green markers denote the locations of households}
    \label{map:regions}
\end{figure}

Table \ref{tbl:summary} shows a set of summary statistics for our sample. The mean parcel size for a household is about 0.15 Ha, with a maximum size of a little less than 1.5 Ha. Harvest labor is disproportionately skewed to family participation with around 20 days of harvest labor being conducted by family members and only about 2 days for hired labor. This

\input{results/tables/summary}
